The {TestIdeals} package for \emph{Macaulay2}

### 2019-04-28 Fsing/TestIdealsPaper/TestIdeals.tex
Small changes
Changes in examples of paper

\documentclass{amsart}
\usepackage{calc,amssymb,amsthm,amsmath}
%\usepackage{mathtools}
\RequirePackage[dvipsnames,usenames]{xcolor}

@@

% TODO NOTES
\usepackage[textwidth=3.5 cm,textsize=small,shadow,
%disable
%%option disable removes the notes
]{todonotes}

\newcommand{\warning}[2][]
{\todo[color=red,caption={},#1]{#2}}
\newcommand{\details}[2][]
{\todo[linecolor=cyan,backgroundcolor=cyan!40, caption={},#1]{#2}}
\newcommand{\postit}[2][]
{\todo[linecolor=orange,backgroundcolor=yellow!40, caption={},#1]{#2}}
\newcommand{\myexample}[2][]
{\todo[linecolor=green,backgroundcolor=green!50,caption={}, #1]{#2}}
\newcommand{\flag}[2][]
{\todo[linecolor=orange,backgroundcolor=yellow, caption={},#1]{#2}}
\newcommand{\oldargument}[2][]
{\todo[linecolor=darkgray,backgroundcolor=gray!40, caption={},#1]{#2}}
\newcommand{\myquestion}[2][]
{\todo[linecolor=purple,backgroundcolor=purple!80,caption={}, #1]{#2}}
\newcommand{\answer}[2][]
{\todo[noline, backgroundcolor=white, bordercolor=purple, caption={},#1]{#2}}
\newcommand{\pedro}[2][]
{\todo[linecolor=blue,backgroundcolor=blue!10,caption={}, #1]{#2}}
\newcommand{\billy}[2][]
{\todo[linecolor=green,backgroundcolor=green!10,caption={}, #1]{#2}}
\newcommand{\bob}[2][]
{\todo[linecolor=purple,backgroundcolor=purple!20,caption={}, #1]{#2}}
\newcommand{\jimmy}[2][]
{\todo[linecolor=orange,backgroundcolor=orange!10,caption={}, #1]{#2}}

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];
i2 : I = ideal(x^6*y*z + x^2*y^12*z^3 + x*y*z^18);
o2 : Ideal of R
i3 : frobeniusPower(1/5, I)
                2   3
o3 = ideal (x, y , z )
o3 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];
i2 : f = x^3 + y^3 + z^3;
i3 : u = f^(5 - 1);
i4 : frobeniusRoot(1, ideal u)
o4 = ideal (z, y, x)
o4 : Ideal of S

i5 : S = ZZ/7[x,y,z];
i6 : f = x^3 + y^3 + z^3;
i7 : u = f^(7 - 1)
i8 : frobeniusRoot(1, ideal u)
o8 = ideal 1
o8 : Ideal of S
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 3;
i2 : R = ZZ/p[x,y];
i3 : m = monomialIdeal(x, y);
o3 : MonomialIdeal of R
i4 : I = m^5;
o4 : MonomialIdeal of R
i5 : t = 3/5 - 1/(5*p^3);
i6 : frobeniusPower(t, I)
             2        2
o6 = ideal (y , x*y, x )
o6 : Ideal of R
i7 : frobeniusPower(t - 1/p^5, I)
o7 = ideal (y, x)
o7 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i8 : S = ZZ/3[a..f,x,y];
i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;
i10 : testIdeal(t, G)
              2        2
o10 = ideal (y , x*y, x )
o10 : Ideal of S
i11 : testIdeal(t - 1/p^5, G)
o11 = ideal (y, x)
o11 : Ideal of S
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 2;
i2 : R = ZZ/p[a,b,c,d];
i3 : I = intersect(ideal(a, b),ideal(a, c),ideal(c, d),ideal(c + d, a^3 + b*d^2));
o3 : Ideal of R
i4 : f = inducedMap(R^1/I, R^1/frobenius(I));
o4 : Matrix
i5 : E2 = Ext^2(f, R^1)
o5 = {-8}  | a4+abc2+abcd a2b            |
     {-10} | a2cd3        a3cd+a3d2+bcd3 |
o5 : Matrix
i6 : target E2
o6 = cokernel {-8}  | 0     a2 b2c2 |
              {-10} | c2+d2 d4 a4d2 |
                            2
o6 : R-module, quotient of R
i7 : source E2
o7 = cokernel {-4} | 0   a  bc  |
              {-5} | c+d d2 a2d |
                            2
o7 : R-module, quotient of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i8 : U = matrix entries E2;
             2       2
o8 : Matrix R  <--- R
i9 : A = matrix entries relations source E2;
             2       3
o9 : Matrix R  <--- R
i10 : frobeniusRoot(1, U)
o10 = {-2} | 1 0 0 |
      {0}  | 0 d a |
              2       3
o10 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i11 : V = ascendModule(1, A, U)
o11 = | 0   a  bc  |
      | c+d d2 a2d |
              2       3
o11 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

>>>>

\documentclass{amsart}
\usepackage{calc,amssymb,amsthm,amsmath,setspace}
%\usepackage{mathtools}
\RequirePackage[dvipsnames,usenames]{xcolor}

@@

@@

\medskip
{\small
\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];

i2 : I = ideal(x^6*y*z + x^2*y^12*z^3 + x*y*z^18);

o2 : Ideal of R

i3 : frobeniusPower(1/5, I)

                2   3
o3 = ideal (x, y , z )

o3 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];

i2 : f = x^3 + y^3 + z^3;

i3 : u = f^(5-1);

i4 : frobeniusRoot(1, ideal u)

o4 = ideal (z, y, x)

o4 : Ideal of S

i5 : S = ZZ/7[x,y,z];

i6 : f = x^3 + y^3 + z^3;

i7 : u = f^(7-1);

i8 : frobeniusRoot(1, ideal u)

o8 = ideal 1

o8 : Ideal of S
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i1 : p = 3;

i2 : R = ZZ/p[x,y];

i3 : m = monomialIdeal(x, y);

o3 : MonomialIdeal of R

i4 : I = m^5;

o4 : MonomialIdeal of R

i5 : t = 3/5 - 1/(5*p^3);

i6 : frobeniusPower(t, I)

             2        2
o6 = ideal (y , x*y, x )

o6 : Ideal of R

i7 : frobeniusPower(t - 1/p^5, I)

o7 = ideal (y, x)

o7 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i8 : S = ZZ/3[a..f,x,y];

i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;

i10 : testIdeal(t, G)

              2        2
o10 = ideal (y , x*y, x )

o10 : Ideal of S

i11 : testIdeal(t - 1/p^5, G)

o11 = ideal (y, x)

o11 : Ideal of S
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
   \setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/2[a,b,c,d];

i2 : I = intersect(ideal(a,b),ideal(a,c),ideal(c,d),ideal(c+d,a^3+b*d^2));

o2 : Ideal of R

i3 : f = inducedMap(R^1/I, R^1/frobenius(I));

o3 : Matrix

i4 : E2 = Ext^2(f, R^1)

o4 = {-8}  | a4+abc2+abcd a2b            |
     {-10} | a2cd3        a3cd+a3d2+bcd3 |

o4 : Matrix

i5 : target E2

o5 = cokernel {-8}  | 0     a2 b2c2 |
              {-10} | c2+d2 d4 a4d2 |

                            2
o5 : R-module, quotient of R

i6 : source E2

o6 = cokernel {-4} | 0   a  bc  |
              {-5} | c+d d2 a2d |

                            2
o6 : R-module, quotient of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i7 : U = matrix entries E2;

             2       2
o7 : Matrix R  <--- R

i8 : A = matrix entries relations source E2;

             2       3
o8 : Matrix R  <--- R

i9 : frobeniusRoot(1, U)

o9 = {-2} | 1 0 0 |
     {0}  | 0 d a |

              2       3
o9 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i10 : V = ascendModule(1, A, U)

o10 = | 0   a  bc  |
      | c+d d2 a2d |

              2       3
o10 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip
